Global code motion of congruent instructions

### 2017-04-17 paper.tex
section refs

The GCM pass can be broadly divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates (congruent instructions) suitable for code-motion,
\item compute a point in the program where it is both legal and profitable to
  move the code,
\item move the code to hoist point or sink point, and
\item update data structures to continue iterative code motion.
\end{itemize}

@@

\subsection{Profitability check (Cost models)}
\label{sec:cost-models}
After the legality checks have passed, we check if a code-motion is profitable.
That takes into account the impact code-motion would have on various parameters
that might affect runtime performance, e.g., impact on live-range, gain in the
code size. Since this is mostly a code-size optimization pass, the goal is to
not regress in performance across popular benchmarks and at the same time to reduce
code size as much as possible. Following are the cost models which are
implemented:

@@

Spills are listed in Table~\ref{tab:spills}. Spills were reduced by an average
of 2\% on the \SPEC{} benchmark suite. This is a result of cost-model which
limits the code-motion to those candidates which do not increase the register
pressure (except for loads Section~\ref{sec:cost-models}, overall spills still
decreases.

@@

\section{Conclusion and Future Work}
\label{sec:future-work}
We have presented the global code motion of congruent computations in SSA
form. We saw that it improves inlining and LICM opportunities, reduces register
spills, it also improves performance in some cases. To preserve performance and
not hoist too much we have register pressure aware cost models described in
Section~\ref{sec:cost-models}. A part of this implementation is already merged
in LLVM trunk as GVNHoist.cpp. We will post the GCM implementation for review.

>>>>

The GCM pass can be broadly divided into the following steps that we will
describe in the rest of this section:
\begin{itemize}
\item find candidates (congruent instructions) suitable for code-motion (Section~\ref{subsec:finding-candidates}),
\item compute a point in the program where it is both legal
  (Section~\ref{subsec:legality}) and profitable
  (Section~\ref{subsec:cost-models}) to move the code,
\item move the code to hoist point or sink point
  (Section~\ref{subsec:optimistic}), and
\item update data structures to continue iterative code motion.
\end{itemize}

@@

\subsection{Profitability check (Cost models)}
\label{subsec:cost-models}
After the legality checks have passed, we check if a code-motion is profitable.
That takes into account the impact code-motion would have on various parameters
that might affect runtime performance, e.g., impact on live-range, gain in the
code size. Since this is mostly a code-size optimization pass, the goal is to
not regress in performance across popular benchmarks and at the same time to reduce
code size as much as possible. Following are the cost models which are
implemented:

@@

Spills are listed in Table~\ref{tab:spills}. Spills were reduced by an average
of 2\% on the \SPEC{} benchmark suite. This is a result of cost-model which
limits the code-motion to those candidates which do not increase the register
pressure (except for loads Section~\ref{subsec:cost-models}, overall spills
still decreases.

@@

\section{Conclusion and Future Work}
\label{sec:future-work}
We have presented the global code motion of congruent computations in SSA
form. We saw that it improves inlining and LICM opportunities, reduces register
spills, it also improves performance in some cases. To preserve performance and
not hoist too much we have register pressure aware cost models described in
Section~\ref{subsec:cost-models}. A part of this implementation is already merged
in LLVM trunk as GVNHoist.cpp. We will post the GCM implementation for review.
